Tables with \textbf{xtable} and \textbf{knitr}

### 2016-10-09 src/ArticleReadyTableGenerate.Rnw
added table generation for pooled LCDM

<<Pooled_Stat_Tests, cache=TRUE,echo=FALSE>>=
  DATA_DIR = "./data/pooled_analysis/"
  sides =  c("lh","rh")
  regions = c("itg","mtg","stg","antcing","postcing")
  conditions  = c("normal","aMCI","amdMCI","nMCI","nmdMCI")
  comparisons = t(array(c(1,2,1,3,1,4,1,5,2,3,2,4,4,5),dim = c(2,7)))
  hypothesis_ordinality <- c("two.sided","less","greater")

@@

>>>>

<<Pooled_Stat_Tests, cache=TRUE,echo=FALSE,warning=FALSE>>=
  DATA_DIR = "./data/pooled_analysis/"
  sides =  c("lh","rh")
  regions = c("itg","mtg","stg","antcing","postcing")
  conditions  = c("normal","aMCI","amdMCI","nMCI","nmdMCI")
  comparisons = t(array(c(1,2,1,3,1,4,1,5,2,3,2,4,4,5),dim = c(2,7)))
  hypothesis_ordinality <- c("two.sided","less","greater")

@@

<<echo=FALSE, results='asis' >>=

  cond_1 = conditions[comparisons[,1]]
  cond_2 = conditions[comparisons[,2]]
  comparison_strings <- paste(cond_1,cond_2, sep =" vs ")
  test_names <- c("KS test","MWU test", "Welch's t-test")
  col_names <- outer(hypothesis_ordinality,test_names,paste,  sep=".")
  p_value_table_names <-expand.grid(comparison_strings, col_names)
  p_value_table <- matrix(0,nrow = 7,ncol = 9)

  for (side in sides){
    for ( i in 1:7 ) {
      for (j in 1:3){
        test.type <-  hypothesis_ordinality[j]
        for (k in 0:2){
          test.name <- names(pooled_test_results[[i]][[test.type]][(k+1)])
        p_value_table[i,j + (k*3)] <- pooled_test_results[[i]][[test.type]][[test.name]]$p.value

        }
      }

    }
  }
  colnames(p_value_table)<- col_names
  xtab.out <- xtable(p_value_table)
  addtorow <- list()
  addtorow$pos <- list(0)
  addtorow$command <- paste0(paste0('& \\multicolumn{3}{c}{', c("KS test","MWU test", "Welch's t-test"), '}', collapse=''), '\\\\')
  print.xtable (xtab.out, add.to.row = addtorow, only.contents=TRUE,
    include.rownames=FALSE,
    type="latex")
# create a table of 7 comparisons
#
